\documentclass[12pt, a4paper]{article}             % use "amsart" instead of "article" for AMSLaTeX format
\usepackage[a4paper,margin=1in]{geometry}          % Adjust margins
\usepackage{amsmath,amssymb,listings,color}        % Math packages: amsmath, amssymb, listings, color
\usepackage[makeroom]{cancel}

\title{\bf{Getting Started with \LaTeX}}
\author{Author: David Oniani
\\
\ \ \ Instructor: Tommy Occhipinti}
\date{September 13, 2018}

\usepackage{listings}
\usepackage{color}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstset{
backgroundcolor=\color{backcolour},
aboveskip=3mm,
belowskip=3mm,
showstringspaces=false,
columns=flexible,
basicstyle={\small\ttfamily},
numbers=left,
numberstyle=\normalsize\color{gray},
keywordstyle=\color{blue},
commentstyle=\color{dkgreen},
stringstyle=\color{mauve},
breaklines=true,
breakatwhitespace=true,
tabsize=4
}


\begin{document}
\maketitle


\begin{enumerate}
\item[15.]
Prove the following statement is false by providing a counterexample: If $n \in \mathbb{Z}^+$ is odd
and $n > 1$ then there exists a non-negative integer $i$ and a prime $p$ such that $n = 2^i + p$.
\\

\begin{quote}
This is the type of statement where "for every" part is hidden. In other words,
the statement could be translated in the following way: "For every $n > 1 \in \mathbb{Z}^+$
there exists a non-negative integer $i$ and a prime $p$ such that
$n = 2^i + p$".
\end{quote}

Thus, all we have to do is find an integer $n > 1$, $i \in \mathbb{Z}^+$, and $p \in \mathbb{P}$ where $\mathbb{P}$ is a set
of prime numbers. Now, notice that $n = 2$ is a counterexample. If $n = 2$, then $i$ has to be either 0 or 1 (since $i$ is non-negative and
if $i > 1$, $2^i > 2$ and the equality will not hold).
Hence, for $n = 2$, we have $i = 0$ or $i = 1$. Let's only consider the first example.
If $n = 2$ and $i = 0$, $2^i = 1$ and $p$ has to be 1 which is not prime. Thus, we found $n$ for which the statement is false which
proves that the initial statement is indeed false.
\begin{flushright}
\textit{Q.E.D.}
\end{flushright}

\item[16.]
Prove the following statement is false by providing a counterexample:
If S and T are shifty sets (in the sense of a previous exercise), then $S \cap T$ is also a shifty set.
\begin{quote}
Definition of the shifty set: A subset $S$ of $\mathbb{Z}$ is called \textit{shifty} if for every $x \in S, \ x-1 \in S \ \textnormal{or} \ x + 1 \in S$.\\

Suppose $S$ and $T$ and shifty. Let $S = \{1,2,4,5\}$ and $T = \{2,3,6,7\}$.
Then $S \cap T = \{2\}$ and $1, 3 \notin S \cap T$ so we found an example for which
$S$ and $T$ are shifty, but $S \cap T$ is not.
\begin{flushright}
\textit{Q.E.D.}
\end{flushright}
\end{quote}

\item[17.]
Prove that if $x$ is odd, then $x^3$ is odd.

\begin{quote}
Suppose $x$ is odd. Then, by the definition of an odd number, we have:
$$x = 2k + 1, \ \textnormal{where} \ k \in \mathbb{Z}$$
Now, we can plug $2k + 1$ into $x^3$. We get:
$$
x = (2k + 1)^3 = 8k^3 + 12k^2 + 6k + 1 = 2 \times (4k^3 + 6k^2 + 3k) + 1
$$

Let's introduce a new variable $l$ and set it equal to $(4k^3 + 6k^2 + 3k)$.
Then we can rewrite $x$ as $x = 2l + 1$. Finally, we conclude that since
$(4k^3 + 6k^2 + 3k) \in \mathbb{Z}$, $l \in \mathbb{Z}$ and $2l + 1$ is odd which
means that $x$ is also odd.
\end{quote}

\item[18.]
Suppose that $m$ and $n$ are doubly even (in the sense of an earlier exercise):
\begin{quote}
Definition of the \textit{doubly even} integer: An integer $n$ is called doubly even if there exist even integers $x$ and $y$ such that $n = xy$.\\

\begin{itemize}
\item[a.]
Prove that $mn$ is doubly even.
\begin{quote}
Suppose $m$ and $n$ be doubly even integers, then we know that both of them are even (as they both are the multiplications of even integers).
Thus, according to the definition, $mn$ is doubly even since it is the multiplication of two even integers.
\end{quote}

\item[b.]
Prove that $m + n$ is doubly even
\begin{quote}
Suppose $m$ and $n$ be doubly even integers, then we know that both of them are even (as they both are the multiplications of even integers).
Let $m = 2a \times 2b$ and $n = 2c \times 2d$, where $a,b,c,d \in \mathbb{Z}$. Then $m + n = 4ab + 4cd = 2 \times (2ab + 2cd)$. Hence, we managed to represent
$m + n$ as the multiplication of two even integers ($2$ and $2ab + 2cd$) and this proves that $m + n$ is doubly even.
\end{quote}
\end{itemize}
\begin{flushright}
\textit{Q.E.D.}
\end{flushright}
\end{quote}

\item[19.]
Prove that if $m$ is even but not doubly even then $m + 2$ is doubly even.
\begin{quote}
Let's first analyze what it means to be even but not doubly even. As we know, an integer
is doubly even if and only if it can be represented as a multiplication of two even integers.
This means that doubly even integer is always divisible by 4. So what would be integers which are even
but not doubly even? Those are the integers which are divisible by 2 but not by 5 (e.g., 2,6,10 etc.).
Then we let $m = 4k + 2$, where $k \in \mathbb{Z}$. We get $m + 2 = 4k + 2 + 2 = 2 \times (2k + 2)$.
Hence, we represented $m + 2$ as a multiplication of two even integers which proves that $m + 2$ is
doubly even.
\begin{flushright}
\textit{Q.E.D.}
\end{flushright}
\end{quote}

\item[20.]
Prove or Disprove: if $A$ and $B$ are sets then there exists a set $C$ such that $A \cup B = A \cup C$.
\begin{quote}
It is right so let's prove it.
Suppose $C = B$, then we can rewrite $A \cup C$ as $A \cup B$ and we get $A \cup B = A \cup B$.
We know that $A \cup B$ is a set itself so let's set it equal to $D$. Finally, we get $D = D$ which
is true.
\end{quote}
\begin{flushright}
\textit{Q.E.D.}
\end{flushright}
\end{enumerate}

\end{document}
