---
title: "Math 328 Chapter 6 HW Part B"
author: "David Oniani"
date: "March 07, 2021"
output: word_document
---

<!-- Exercises 6.30, 6.32, and 6.36. -->

## Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(Stat2Data)
library(dplyr)
library (tidyr)
library(emmeans)
library(ggplot2)

# I like the minimal theme
theme_set(theme_minimal())

# Disable warnings (they clutter the document)
options(warn = -1)
```

## Exercise 6.30

```{r}
data("RiverIron")

# (a) Fit the two-way additive model
RiverIron$grandMean = mean(RiverIron$Iron)
twoWayIron = aov(Iron ~ grandMean + River + Site, RiverIron)
summary(twoWayIron)

# (b) Obtain a normal probability plot of residuals
plot(twoWayIron, which = 2)

# (c) Obtain a plot of residuals versus fitted values
plot(twoWayIron, which = 1)

# (d) Estimate the fitted value from the graph
xval = twoWayIron$fitted.values[9]
yval = twoWayIron$residuals[9]
print(c(xval, yval))
```

a. After fitting the two-way additive model, we get that the F-score and p-value
   for River are 7.041 and 0.0172 respectively. F-score and p-value for Site are
   8.613 and 0.0172 respectively.
b. Since the points are, for the most part, aligned with the dotted line, it
   seems like the normality assumption for ANOVA is not violated. That being
   said, it is true that some points are visibly outside the dotted line, but
   this is more of a judgment call and for me, it seems to be approximately
   normal.
c. It seems like the variation is not constant. Ideally, the plot should show a
   random scattering of points above and below the reference line at a
   horizontal 0. However, in this case, it does seem that there is some pattern
   in the data. The curvature seems to be unmistakably present.
d. Eyeballing the leftmost fitted value, I could see the point (-135, 165).
    After estimating the point using R, we get that the point is
    (-137.5833, 167.5833). The reason it suggests that this point strongly
    suggests that the model is inappropriate is that they are both very similar.
    Their decimal expansions do not seem random as all 4 digits match.

## Exercise 6.32

```{r}
data("Contraceptives")

# (a) Create the Anscombe plot for this dataset
OralContraceptives = pivot_wider (Contraceptives,
                                  id_cols = "ID",
                                  names_from = "Treatment",
                                  values_from = "EE")

anscombe.plot = function (yvar, xvar) {
  yname = deparse (substitute (yvar))
  xname = deparse (substitute (xvar))
  plot (yvar ~ xvar, ylab=yname, xlab=xname)
  apfit = lm (yvar ~ xvar)
  apfit
  abline (apfit)
  abline (0, 1, lty=2)
  return (apfit)
}

with (OralContraceptives, anscombe.plot (Drug, Placebo))
```

a. You can see the generated plot above in the document. The slope is 0.9243.

b. As we got that the slope is "close" to 1 (with the actual value of 0.9243),
   we can apply the randomized complete block additive model (RCB additive
   model) and thus, there is no need for a transformation.

## Exercise 6.36

```{r}
data("Alfalfa")

# (a)
df = Alfalfa$Ht4
mean_df = mean(df)
sd_df = sd(df)

print(mean_df)
print(sd_df)

twoWayAlfalfa = aov(Ht4 ~ Acid + Row, Alfalfa)

# (b)
# ANOVA
summary(twoWayAlfalfa)

# (c)
# Residual analysis
par(mfrow = c(1,2))
plot(twoWayAlfalfa, which = 1:2)
par(mfrow = c(1,1))
```

(a) The average for the growth in all 15 cups is 1.74 and the standard deviation
    for the growth in all 15 cups is approximately 1.11.
(b) Performed the ANOVA (see the code above).
(c) We can see that the acids are all independent of each other and thus,
    the condition for independence holds. From Residuals vs Fitted plot, we
    see that the red line is does not necessarily align with the black
    dotted line and is not flat. This means that there is some non-linear
    trend to the residuals. In the Normal QQ plot, we see that there are
    some data points that deviates form the dotted line. Hence, not all
    ANOVA conditions are met.
(d) Based on the ANOVA table, we can conclude that there is a significant
    difference in average growth due to the treatments. This is the case
    since the p-value is significant (0.0487 < 0.05).
(e) Based on the ANOVA table, we cannot conclude that there is a significant
    difference in average growth due to the distance from the window. This
    is the case since the p-value is not significant (0.3235 > 0.05).
