---
title: "Math 317 - Chapter 14 Homework 1"
author: David Oniani
date: \today
output: pdf_document
---

Plot the logistic mean function,
$E\{Y\}=exp(\beta_0+\beta_1 X_1)/(1+exp(\beta_0+\beta_1 X_1))$, when
$\beta_0=-25$ and $\beta_1=0.2$.

```{r}
library(ggplot2)

X = seq (90, 150)

sigmoid = function(x) {
  exp(-25 + 0.2 * x) / (1 + exp(-25 + 0.2 * x))
}

ggplot(data.frame(x=X), aes(x=x)) +
      stat_function(fun=sigmoid, geom="line") +
      xlab("x") + ylab("y")
```

What is the predicted proabability for X=115?

```{r}
print(sigmoid(115))
```

For what value of X is the mean response equal to 0.5?  (Solve for X
algebraically, then calculate in R)

```{r}
# The formula is $X = (ln(P / (1 - P)) - B_0) / B_1$
print((log(0.5 / (1 - 0.5)) - (-25)) / 0.2)
```

Find the odds when $X=130$, when $X=131$, and the odds ratio for X=131 vs.
X=130.  Verify that this odds ratio is equal to $exp(\beta_1)$.

```{r}
# The odds formula is $p / (1 - p)$
odds = function(x) {
  x / (1 - x)
}

odds130 = odds(sigmoid(130))
odds131 = odds(sigmoid(131))

oddsRatio = odds131 / odds130

print(oddsRatio)
print(exp(0.2))

# Odds ratio and beta_1 are equal (at least within 12 decimal points)
print(round(oddsRatio, 12) == round(exp(0.2), 12))
```

A psychologist conducted a study to examine the nature of the relation,
if any, between an employee's emotional stability (X) and the employee's
ability to perform in a task group (YJ. Emotional stability was measured by a
written test for which the higher the score, the greater is the emotional
stability. Ability to perform in a task group (Y = 1 if able, Y = 0 if unable)
was evaluated by the supervisor.

```{r}
taskperf = c(0, 0, 0, 1, 1, 0, 0, 1, 1,
             1, 1, 1, 1, 0, 1, 0, 1, 0,
             1, 0, 0, 0, 1, 0, 1, 0, 1)

emostab = c(474, 432, 453, 481, 619, 584, 399, 582, 638,
            624, 542, 650, 553, 425, 563, 549, 498, 520,
            610, 598, 491, 617, 621, 573, 562, 506, 600)

plot (emostab, taskperf, xlab="Emotional Stability", ylab="Task Performance")
lines (lowess (taskperf ~ emostab), col='red')
logistic.fit = glm (taskperf ~ emostab, family=binomial)
summary (logistic.fit)

emostab.seq = seq(400, 650, by=5)
X <- cbind(1, emostab.seq)
betahat = coefficients(logistic.fit)
Xb <- X %*% betahat
prob <- exp(Xb)/(1+exp(Xb))

lines(emostab.seq, prob, col='blue')
```

Obtain $exp(\beta_1)$ and interpret that number.

```{r}
# Obtaining exp(beta_1) value
print(exp(0.018920))
```

$exp(b_1) = 1.0191$. This means that the odds of employee's estimated task
performance increases by 1.91% (1.91 percent) with each additional unit increase
in employee's emotional stability.
