---
title: "Math 328 Chapter 8 HW - Part A"
author: "David Oniani"
date: "April 11, 2021"
output: word_document
---

<!-- Do Exercises  8.2, 8.14, 8.18, and 8.26, using R Markdown. -->

## Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(Stat2Data)
library(agricolae)
library(emmeans)
library(mosaic)
library(multcomp)
```

## Exercise 8.2

In case of two-way ANOVA, we must apply Levene’s test to groups of data formed
by the cells (i.e., the combinations of levels of factors), rather than to
groups formed by levels of a single factor. In this case, Levene's test was
applied to groups by levels of Factor A (single factor) and Factor B (single
factor) separately and thus, such application of Levene's test would not be
appropriate.

## Exercise 8.14

```{r}
# Load the data
data("SeaSlugs")

# a) Use Fisher’s LSD intervals to find any differences that exist between the
#    percent of larvae that metamorphosed in the different water conditions.
fit1 <- aov(Percent ~ factor(Time), SeaSlugs)
anova(fit1)
print(agricolae::LSD.test(fit1, "factor(Time)"))

# b)  Use Tukey’s HSD intervals to find any differences that exist between the
#     percent of larvae that metamorphosed in the different water conditions.
fit2 <- aov(Percent ~ factor(Time), SeaSlugs)
TukeyHSD(fit2)

# c) Were your conclusions to (a) and (b) different? Explain. If so, which
#    would you prefer to use in this case and why?
# 
# No code needed, see the response below
```

a) Means with the same letter seem to be different at intervals 0, 5, and 25 as
   compared with those at intervals 20, 15, and 10. Other than this, there does
   not seem to be any significant differences between the time intervals 20, 15,
   and 10 and other time intervals.

b) It seems like intervals 0 - 10, 0 - 15, 0 - 20, and 0 - 25 are the most
   significant. Hence, there are differences between the percent of larvae that
   metamorphosed in the different water conditions.
   
c) Conclusions in (a) and (b) are indeed different. Fisher's LSD seems to be
   narrower than Tukey's HSD. Since in Fisher's LSD we are likely to have a
   higher risk of making Type I error, I would prefer Tukey's HSD in this case.

## Exercise 8.18

```{r}
# Load the data
data("Blood1")

# a) What are the hypotheses that describe the test we would like to
#    perform?
fit1 <- aov(SystolicBP ~ Overwt, Blood1)
summary(fit1)

# b) Write the contrast of interest in symbols and compute its estimated
#    value.
ms = mean(SystolicBP ~ Overwt, data=Blood1)
cc = c(1, -0.5, -0.5)
contrast = sum(ms * cc)
contrast

# c) What is the standard error of the contrast?
mse = summary(fit1)[[1]]$"Mean Sq"[2]
ns = tally(~Overwt, data=Blood1)
se = sqrt(mse * sum(cc^2 / ns))
se

# d) Perform the hypothesis test to test the alternative hypothesis that the
#    mean systolic blood pressure is different for people of normal weight, as
#    compared to people who are overweight or obese. Be sure to give your
#    conclusions.
t1 = contrast / se
errordf = fit1$df.residual
pvalue1 = 2 * pt(t1, errordf)
pvalue1
```

a) Since we want to compare levels of systolic blood pressure based on weight
   status, one-way ANOVA would be appropriate. Hence, we would perform a one-way
   ANOVA for systolic blood pressure by weight status. The model and its summary
   statistics are shown above.

b) Since we are comparing normal to overweight and obese, we can set normal to
   1 and both overweight and obese to -0.5. Hence, the equation will be
   1 * y_normal - 0.5 * y_overweight - 0.5 * y_obese with
   1 + (-0.5) + (-0.5) = 0 which satisfies the condition that all coefficients
   add up to 0. After calculating the contrast, we got the value of
   approximately -12.459.

c) After calculating the standard error of the contrast, we got that its value
   is approximately 2.543.

d) After performing the hypothesis test, we got the p-value of 1.30648e-06
   which is a lot smaller than the 0.05 cutoff. This means that difference is
   significant and hence, we reject the null and accept alternative, effectively
   concluding that there is a significant difference of systolic blood pressure
   based on weight status (normal vs overweight or obese).

## Exercise 8.26

```{r fig.height=3.5, fig.width=5}
# Load the data
data("Pulse")

# a) Create one or more graphs to assess the conditions required by ANOVA.
#    Comment on why the Kruskal-Wallis test might be more appropriate
#    than an ANOVA.
fit1 <- aov(Active ~ ., Pulse)
plot(fit1)

# b) Run the Kruskal-Wallis test and report the results and conclusions
kruskal.test(Active ~ Exercise, Pulse)
```

(a) Residuals vs Fitted shows a constant variance and the red line follows the
    dotted line closely. Hence, based on Residuals vs Fitted plot, the equal
    variance condition does not seem to be violated (i.e., the equal variance
    condition is met). The normality condition does not seem to bet met. While
    most of the points in the middle of the Normal Q-Q do seem to follow the
    dotted line, there is a significant deviation at both ends. Thus, based on
    the Normal Q-Q plot, we can conclude that the normality assumption is not
    met and therefore, is violated. The Scale-Location plot does not show a
    decreasing trend. Residuals vs Leverage plot does not show any obvious
    outliers. Although the variance condition is met, the normality assumption
    is not. If the normality assumption was not violated, using ANOVA would be
    appropriate, but since it is, Kruskal-Wallis test is more appropriate.
    Hence, Kruskal-Wallis test is more appropriate since the normality
    assumption is not met.
    
    NOTE: We fitted the full model response vs all variables. The book was a bit
          ambiguous about the exact kind of model they wanted us to fit. That
          being said, I have also rechecked a model
          `fit1 <- aov(Active ~ Exercise)` and the normality assumption is still
          being violated (i.e., is not met).

b) After performing the Kruskal-Wallis test, we get that the Kruskal-Wallis
   chi-squared value is 29.826 with the p-value of 3.337e-07 and 2 degrees of
   freedom. Now, since the p-value is significantly lower than the 0.05 cutoff,
   we reject the null hypothesis of no difference in the pulse rates (Activity
   variable) and conclude that there are different pulse rates, depending on
   exercise given to students.
