---
title: "Math 328 Chapter 8 HW Part 2.Rmd"
author: "Dr. Phil"
date: "April 17, 2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise 8.38

Music Time: Descriptive.

Participants were asked to judge when 45 seconds had passed under three
conditions:

* Silence
* Listening to an upbeat song
* Listening to a calm song

The order in which each subject experienced these three conditions was randomized.

The response is Accuracy, which is the absolute difference between the reported
time and 45 seconds.  Use the square root transformation of Accuracy.

### 8.38 (a) Boxplots

```{r fig.height=3.5, fig.width=4}
library (Stat2Data)
data ("MusicTime")
str (MusicTime)
boxplot (sqrt(Accuracy) ~ Music, data=MusicTime)
```

Comments on the plot: It seems like the sqrt(Accuracy) is, on average, higher
when listening to a calm song. The median value seems to be the biggest in this
case. sqrt(Accuracy) looks approximately the same when listening in silence
(control) or upbeat music. That being said, it does seem like listening in
silence (control) has slightly bigger sqrt(Accuracy) value. The median value of
listening in silence (control) seems to be bigger than that of listening to
upbeat as well. Hence, the median values show the following descending order:
calm, control, upbeat.


### 8.38 (b)

The null hypothesis is: 45 seconds passed at the same time with all three types
of music (i.e., accuracy was the same in all three cases).

In symbols, H_0: acc_1 = acc_2 = acc_3 or H_0: u_1 = u_2 = u_3.




### 8.38 (c)

Answer: The boxplots do provide the visual evidence against the null hypothesis.
This is the case since, clearly, sqrt(Accuracy) was the largest when listening
to the calm music. Furthermore, sqrt(Accuracy) was noticeably larger when
listening to a calm music than listening to any other type of music
(silence/control or upbeat).



## Exercise 8.40

Conduct a repeated measures ANOVA.

```{r}
mt1 = aov (sqrt(Accuracy) ~ Music + Error (Subject), data=MusicTime)
summary (mt1)
library (emmeans)
summary (emmeans (mt1, pairwise ~ Music), infer=c(T,T))
```

Conclusions: from the very get-go, we can see that the p-value (approximately,
0.004, which is less than the 0.05 cutoff) from the summary of aov is
significant meaning that there is a significant evidence against the null
hypothesis that average accuracy for detecting when 45 seconds have passed was
the same for all three types of music. Further analysis using emmeans functions
shows that the difference between calm and upbeat has the smallest p-value of
approximately 0.007 and therefore, is significant, which was expected based on
our ordering in exercise 8.38 (decreasing order: calm, control, upbeat). An
estimated difference calm - upbeat is approximately 1.202. The difference
between calm and control is also significant with the p-value of 0.01 and an
estimate of approximately 1.120. Finally, the difference between control and
upbeat is not significant (an observation that we made in exercise 8.38) with
the p-value of 0.973 and an estimate of approximately 0.083.



## Exercise 8.62

These data are from three car manufacturers.  The task is to model Price as a
function of car type and either age or mileage.

### 8.62 (a)

ANOVA for Price vs car type.

```{r}
data ("ThreeCars2017")
str (ThreeCars2017)
boxplot (sqrt(Price) ~ CarType, data=ThreeCars2017)
cars1 = lm (sqrt(Price) ~ CarType, data=ThreeCars2017)
summary (cars1)
anova (cars1)
```

Findings: The boxplot shows that there is a difference in mean prices in the
three models. More specifically, it looks like Mazda6 has the lower price, on
average, than either Accord or Maxima. The median value of Mazda6 is below those
of Accord and Maxima. Median price of Accord and Maxima seem to be approximately
the same, but the mean value should be higher for Maxima as its box and lower
whisker are clearly above the Accord boxplot. After performing anova on the
fitted model, we also got a significant p-value of approximately 0.01 (< 0.05)
for CarType, meaning that there is likely a significant difference between at
least two car types.


```{r}
summary (emmeans (cars1, pairwise ~ CarType), infer=c(T,T))
```

Findings: We see that the difference between Maxima and Mazda6 is significant
with the p-value of approximately 0.010 and an estimate of 0.611. Differences
Accord - Maxima and Accord - Mazda6 are not statistically significant with the
p-values of approximately 0.611 and 0.104 respectively.


### 8.62 (b)

ANCOVA with car type and age.

```{r}
cars2 = lm (sqrt(Price) ~ CarType + Age, data=ThreeCars2017)
summary (cars2)
anova (cars2)
```

Results: From the summary, we can see that the intercept is significant with the
p-value less than 2e-16. Mazda6 car type is also significant with the p-value of
5.55e-05. Age is significant with the p-value of less than 2e-16. Model Maxima
is not significant with the p-value of 0.662. The ANCOVA model shows that both
CarType and Age are statistically significant with the p-values of 8.554e-11 and
2.2e-16 (in fact, less than 2.2e-16, so Age is very significant) respectively.


```{r}
library (ggplot2)
qplot (Age, sqrt(Price), data=ThreeCars2017, color=CarType) +
  geom_line (aes(y=predict (cars2)), lwd=1)
summary (emmeans (cars2, pairwise ~ CarType), infer=c(T,T))
```

Conclusions: The qplot shows a reasonable pattern suggesting that the older the
car, regardless of the car type, the lower the price. That being said, it seems
like Maxima car type has a lot of younger cars with some of them being fresh and
thus, the prices are high. The oldest Maxima in the dataset is also 10 years
old. Car type Accord has some of the oldest cars (> 15). Mazda6 is similar to
Accord in terms of younger cars, but does not have cars as old as Accord.
Contrasts do not show any significant differences. emmeans shows that the
emmeans for Accord, Maxima, and Mazda6 are 3.74, 3.71, and 3.40 respectively
with the p-value less than 0.0001 in all cases.


### 8.62 (c)

ANCOVA with car type and Mileage.

```{r}
cars3 = lm (sqrt(Price) ~ CarType + Mileage, data=ThreeCars2017)
summary (cars3)
anova (cars3)
```

Results: The summary of the model cars3 shows that the Intercept and Mileage are
both significant with the p-values less than 2e-16 in both cases. ANOVA models
shows that both CarType and Mileage are significant with the p-values of
2.687e-07 and 2.2e-16 (less than 2.2e-16) respectively.




```{r}
qplot (Mileage, sqrt(Price), data=ThreeCars2017, color=CarType) +
  geom_line (aes(y=predict (cars3)), lwd=1)
summary (emmeans (cars3, pairwise ~ CarType), infer=c(T,T))
```

Conclusions: The qplot shows that Accord has some cars with the mileage that is
less than that of any car of either Maxima or Mazda6. Accord also has some cars
with the most mileage. That being said, Accord model contains all mileages from
both Maxima and Mazda6 and hence, we do not expect very significant differences
in contrasts. Maxima and Mazda6 look similar in terms of mileage, but Maxima, on
average, does seem to have cars with smaller mileage than Mazda6 (i.e., Maxima
line is Mazda6 line moved up across y-axis and then shifted left across x-axis).
The contrasts show that emmean for Accord, Maxima, and Mazda6 are 3.60, 3.85,
and 3.41 respectively with all of the p-values less than 0.0001. The contrasts
show that Accord - Maxima difference is marginally significant with the p-value
of approximately 0.05 and an estimate of -0.245. Accord - Mazda6 difference is
not significant as its p-value is approximately 0.16. Maxima - Mazda6 contrast,
however, is significant (as expected) with the p-value of 0.0002 and an estimate
of 0.439.



### 8.62 (d)

Your choice of final model and why?

I would go with cars3 model. This is due to the fact that mileage might be more
important metric of assessing comparing cars than age. One might have a car
which is 10 years old but with no mileage as well as a car that is 1 year old
but with a lot of mileage. Due to the same reason, the car mileage also speaks a
lot to the condition of the car and from a more practical perspective, tells us
that some car models are able to withstand more miles (e.g., while Maxima model
had some of the youngest cars, Accord had some cars whose mileage were clearly
bigger than any other car in Maxima or Mazda6). Hence, mileage can also help us
make decisions if purchasing a particular car model (e.g., maybe Accord is
better as we have some evidence that its cars could drive a lot longer, more
miles, etc).