---
title: "MATH-328 Project"
author: "David Oniani"
date: "April 27, 2021"
output: word_document
---

\tableofcontents

## Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(emmeans)
library(ggplot2)
library(multcomp)
library(sjmisc)
```

## Initial Data Exploration and Analysis

```{r}
# Load the data
data = read.csv("data.csv")

# Get rid of unwanted columns (will come in handy when designing models)
data[c("trt_id", "X_hue", "X_bright", "X_price")] = NULL

# Make hue, bright, and price factors
data$hue    = factor(data$hue)
data$bright = factor(data$bright)
data$price  = factor(data$price)

# Show first 6 and last 6 rows
head(data)
tail(data)

# Show the structure of the data
str(data)

# Are factors crossed?
is_crossed(data$hue, data$bright)
is_crossed(data$hue, data$price)
is_crossed(data$bright, data$price)

# Are factors nested?
is_nested(data$hue, data$bright)
is_nested(data$bright, data$hue)
is_nested(data$hue, data$price)
is_nested(data$price, data$hue)
is_nested(data$bright, data$price)
is_nested(data$price, data$bright)

# Scatterplot matrix
plot(data, pch = 20, cex = 1.5, col = "purple")
```

The data has three categorical variables: hue, bright, and price and one
response variable: quality. We will treat hue, bright, and price as factors. The
dataset is then suitable for a 3-factor experiment of online shopping. It
contains three categorical factors: web page hue (1 = Blue, 2 = Red), Brightness
(1 = Dark, 2 = Bright), and Price (1 = Low, 2 = high). Sample sizes are
unbalanced. We will analyze when and how the response value - perceived quality
- changes with brightness, hue, and price.

Exploratory analysis above prints first and last 6 rows of the data as well as
shows the overall structure of the data. We also made hue, bright, and price
factor variables. This will help using these variables properly, as factors, in
models that we will develop.

Thus, our response variable is quality, which is a perceived quality of the
product. Our predictor variables are hue, bright, and price - all of them are
categorical variables. Since we do not have any quantitative predictors, we do
not have covariates.

Factors hue and bright are crossed. Factors hue and price are also crossed.
Factors bright and price are crossed too.

There is no nesting among the factors.

Since the investigators controlled the levels for all factors, all of the
factors are fixed. Hence, factors hue, bright, and price are fixed (not random).

The scatterplot matrix is also shown. At a first glance, it does not seem to
give us any signficant/important insights, so we can move on with our analysis.

## Fitting Full Model

```{r fig.height=3.5, fig.width=5}
# Fit the initial model with three-way
fit1 = aov(quality ~ .^3, data)

# Report the summary
summary(fit1)

# Estimates
fit1$coefficients

# Residual analysis
par(mfrow = c(1, 2))
plot(fit1, pch = 20, cex = 1.5, col = "purple")
par(mfrow = c(1, 1))
```

We cannot do statistical inference for the full model (including the three-way
interaction) as we have no replicates. However, we can still fit a model
including all two-way interactions.

Residuals vs Fitted plot shows fairly constant variance. The red line follows
the dotted line closely, further corroborating our hypothesis. Thus, the
constant variance assumption is not violated.

The Normal Q-Q plot shows that most of the points, except for at the tails, of
the plot do follow the dotted line. However, at both tails, there is some
deviation from the dotted line which suggests some non-normality. This is more
of a judgment call, but to me it seems to approximately normal. Hence, the
normality assumption for ANOVA is met.

Scale-Location plot does have some decreasing trend toward the end of the plot,
but the variance does seem to be constant.

Residuals vs Leverage does not show any significant outliers.

Given our analysis, let us now perform a Box-Cox analysis in order to find an
appropriate power transformation for the response variable.

```{r}
# Box-Cox analysis for the power transformation
MASS::boxcox(fit1, lambda = seq(0, 2, 0.7))
```

From the plot, we can see that the lambda value is approximately 0.9. This means
that we have two options:

1. Leave the response as is
2. Raise the response to the 0.9 power

We will try raising the response to 0.9 power and see if it helps. In the end,
we will pick the better model.

```{r fig.height=3.5, fig.width=5}
# Refit the model, applying the right power transformation
fit2 = aov(quality^0.9 ~ .^3, data)

# Summary
summary(fit2)

# Estimates
fit2$coefficients

# Residual analysis
par(mfrow = c(1, 2))
plot(fit2, pch = 20, cex = 1.5, col = "purple")
par(mfrow = c(1, 1))
```

After applying the transformation, all four plots look similar and the summary
also shows approximately the same p-values and estimates (coefficients). For
this reason, we will stick with our initial model - fit1.

Since all of our interactions are significant, we do not have any insignificant
interactions to remove and we do not need to apply a stepwise regression to
remove non-significant effects.

## Results

We start by analyzing the interaction plots of significant effects. Since all of
the two-way interactions were significant and we have three factors, we will
analyze three plots. This would also be the highest order interactions as due to
the nature of the study that collected the data, including three-way interaction
would not be appropriate.

```{r fig.height=3.5, fig.width=5}
# Interaction plots
emmip(fit1, hue ~ bright)
emmip(fit1, hue ~ price)
emmip(fit1, bright ~ price)
emmip(fit1, bright ~ price | hue)
```

In terms of interactions plots, all four interaction plots show some degree of
interaction between the variables. The lowest degree of interaction seems to be
between variables hue and price (lines are relatively parallel with respect to
each other). The highest degree of interaction seems to be between variables
bright and price (lines are not relatively parallel with respect to each other).
That being said, in all three plots, two lines would cross each other if
extended and thus, the interactions are significant. Finally, the three-way
interaction plots also show some interactions which can be more difficult to
assess, but the lines are definitely not parallel with respect to each other in
either of the plots (hue: 1 and hue: 2 plots). Further analysis will show the
degree of these interactions in more detail.

```{r}
# Report the summary
summary(fit1)

# Estimates
fit1$coefficients
```

The summary report confirms our conclusions based on interaction plots. Indeed,
hue and price interaction seems to be the least significant one (but still
significant as the p-value is approximately 0.02 < 0.05) with the p-value of
0.02. The interaction between bright and price, as observed, is most significant
with the p-value of approximately 0.004. The interaction between hue and bright
is also significant with the p-value of approximately 0.008. Finally, the
three-way interaction between hue, bright, and price is also significant with
the p-value of approximately 0.02.

Variables hue, bright, and price are all significant with the p-values of
1.84e-07, 1.82e-07, and 9.47e-06 respectively.

The estimate of hue is approximately -0.45. The estimates for bright and price
are -0.38 and 1.25 respectively.

The intercept is approximately 4.03, which means that the mean quality when all
factors are null is 4.03.

```{r}
cld(emmeans(fit1, ~ hue    | bright), Letters=LETTERS)
cld(emmeans(fit1, ~ hue    | price),  Letters=LETTERS)
cld(emmeans(fit1, ~ bright | price),  Letters=LETTERS)

# We compare bright based on levels of price and hue
cld(emmeans(fit1, ~ bright | price | hue),  Letters=LETTERS)
```

Above find the appropriate pairwise comparisons for the significant effects.

Let us first analyze emmeans with hue and bright interaction. We see that the
mean response (quality value) is the lowest with high brightness and red hue
(2.86). The mean response is the highest when brightness is low and hue is blue
(4.66). When bright = 1 (low brightness) and hue = 2 (red), the emmean is
4.25 and when bright = 2 (high brightness) and hue = 1 (blue), the emmean is
4.18.

In hue - price interaction, the highest emmean value is achieved when price is
high and hue is blue, the value is 4.98. The lowest emmean value is when price =
1 (low price) and hue = 2 (red), the value is 3.76. When price is low and hue is
blue, the emmean value is 3.85. When price is high and hue blue, the emmean is
3.76.

In price - bright interaction, the biggest emmean of 5.08 is when bright = 1 and
price = 2 (high brightness and low price). The lowest emmean value is when price
is low and brightness is high (price = 1, bright = 2). When both brightness and
price are low, the emmean is 3.82 and when both price and brightness are high,
the emmean is 3.66.

Analyzing brightness, based on levels of price and hue, we got that the highest
emmean value is with high price, blue hue, and low brightness (price = 2, hue =
1, bright = 1) and the lowest emmean value is 2.64 with the price is high, hue
is red, and brightness is high (price = 2, hue = 1, bright = 2). The rest of the
values are shown in the table.

```{r fig.height=3.5, fig.width=5}
# Hue - Bright
qplot (hue, quality, data = data, color = bright) + 
  stat_summary(fun = mean, geom = "line", aes(group = bright))

# Hue - Price
qplot (hue, quality, data = data, color = price) + 
  stat_summary(fun = mean, geom = "line", aes(group = price))

# Bright - Price
qplot (bright, quality, data = data, color = price) + 
  stat_summary(fun = mean, geom = "line", aes(group = price))

# Bright - Price - Hue
qplot (bright, quality, data = data, color = price) + 
  stat_summary(fun = mean, geom = "line", aes(group = price)) +
  facet_wrap(vars(hue), labeller="label_both")
```

Above find some qplots which are similar to emmip plots that we had previously,
but also shows the data points. Obviously, these plots do not change our
observations in any way as the data and the model are the same, but they do
provide another way of looking at the interactions between the variables.
Similar to the emmip interaction plots, all interactions seem significant as the
lines are not approximately parallel in any of the plots.

Finally, we state several conclusions. In order for me to explain the
conclusions, I will use analogies - high brightness (think blinding
website/packaging/etc), high hue (think same as high brightness, with blue being
less bright/darker and red being brighter/lighter/blinding in extreme cases),
high price (think something that might have high quality, but that would depend
on interaction with hue and brightness).

* Products with high brightness and high hue have the lowest perceived
  quality - makes sense, blinding brightness and high hue does not leave good
  impressions
* Products with low brightness and low hue have the highest perceived
  quality - makes sense low brightness and low hue probably means more elegant
  website and is therefore, more attractive in general)
* Products with high price and low hue have the highest perceived
  quality - makes sense, low hue would probably mean more elegant website and
  high price would mean that the product is probably high quality (hence, higher
  perceived quality)
* Products with low price and high hue have the lowest perceived
  quality: makes sense, low price on already not very elegant looking website
  might be very attractive.
* Products with high price and low brightness have the highest perceived
  quality - makes sense, products presented with low brightness and high price
  will probably look more elegant and attract more users
* Products with high hue and high brightness have the lowest perceived
  quality - makes sense, products presented with blinding colors and low
  price are not very attractive
