---
title: "Chapter 5 Homework Part B"
author: "David Oniani"
date: \today
output: pdf_document
---

\tableofcontents
\clearpage

## Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(MASS)
library(Stat2Data)
library(dplyr)
library(emmeans)
library(ggplot2)

# Use the minimal theme
theme_set(theme_minimal())

# Disable warnings (they clutter the document)
options(warn = -1)
```

## Exercise 5.32

Do Exercise 5.32 as stated. Also, find a suitable response transformation and
and do a one-way ANOVA on that transformed scale. Include residual analysis and
all pairwise group comparisons.

```{r}
# Data
data(Hawks)

# Get rid of rows with NA values in weight. I could probably replace the missing
# values with averages or medians (using imputer, etc), but in this case, will
# just delete these rows.
#
# NOTE: We only need the following columns: Species, Weight


# We first extract the relevant columns
Hawks = Hawks[, c("Species", "Weight")]
              
# We now remove the rows where the value of the Weight column is NA
Hawks = Hawks[which(!is.na(Hawks$Weight)), ]

# Dotplot
ggplot(Hawks, aes(x = Species, y = Weight, fill = Species)) +
    geom_dotplot(binaxis = "y", binwidth = 15,
                 dotsize = 1.25, stackdir = "center") +
    ggtitle("Weights by Species Dotplot") +
    theme(plot.title = element_text(hjust = 0.5))

# Define the linear regression model
lr = lm(Weight ~ Species, data=Hawks)

# Residuals vs Fitted
ggplot(lr, aes(x = .fitted, y = .resid)) +
    geom_point() +
    geom_smooth() +
    geom_hline(yintercept = 0, col = "red", linetype = "dashed") +
    ggtitle("Residuals vs Fitted") +
    theme(plot.title = element_text(hjust = 0.5)) +
    xlab("Fitted values") +
    ylab("Residuals")

# Calculate standard deviation values
Hawks %>%
    group_by(Species) %>%
    summarize(sd.Weight = sd(Weight))
```

\begin{itemize}
    \item[(a)]
        In terms of weight, red-tailed hawks seem to have the largest weight,
        followed by Cooper's hawks species, and finally, the sharp-shinned
        hawks. It seems like the variance is approximately equal across all
        three groups and hence, equal variance assumption of ANOVA is met. In
        order to verify that this is true, we have also shown The Residuals vs
        Fitted plot which confirms constant variance across the groups (the red
        line approximately follows the dotted line).
    \item[(b)]
        ANOVA assumes that the population standard deviations for all levels are
        equal. The approximate standard deviation values we have gotten are 162,
        189, 80.7 for Cooper's, red-tailed, and sharp-shinned hawks
        respectively. These values are not approximately equal and hence, it
        does not meet at least one of assumptions for performing ANOVA.
\end{itemize}

Now, let us find a suitable response transformation and and do a one-way ANOVA
on that transformed scale. We will also include residual analysis and all
pairwise group comparisons.

```{r}
boxcox(lr)

summary(lr)
```

Box-Cox plot has the form of a flipped parabola \((f(x) = -x^2)\). The
\(\lambda\) (lambda) value is approximately 0.4 and is between 0.45 and 0.5 with
95% confidence (default is 95%). These observations suggest the non-normality of
errors in the linear model. Therefore, it is reasonable to perform the square
root transformation of the response variable (Weight). This would help us
normalize the errors as well as address the non-linearity of the distribution.

It is also important to note that approximately 87.5% of the variation in Weight
is explained by Species.

```{r}

# Perform the square root transform
lr = lm(sqrt(Weight) ~ Species, Hawks)
summary(lr)

# Residual analysis
par(mfrow = c(1,3))
plot(lr, which = 1:3)
# Reset
par(mfrow = c(1,1))

# ANOVA
s <- summary(emmeans(lr, pairwise ~ Species, adjust = "none"), infer = c(T, T))
s
```

After performing the square root transformation, we have already gotten better
with all plots. Residuals vs Fitted is better as the black line follows the red
dotted line and the variance is nearly constant. Normal Q-Q plot has also
improved and the distribution is more normal. The Scale-Location plot shows that
the residuals are spread equally along the ranges of predictors and that the
variance is nearly constant. Besides, the absolute value of the square root of
Standardized Residuals show the decreasing trend.

We can also see the adjusted R-squared value of 0.9108 which means that
approximately 91.08% of variation in \(\sqrt{Weight}\) is explained by Species
which is a good improvement over the previous 87.5%.

Our null hypothesis is that the differences of means across the groups are zero
and the alternative hypothesis is that at least one of differences of means is
different from 0. The $contrasts table shows the following results:

```{r}
s$contrast
```

We get that the difference of means between Cooper's hawks and red-tailed hawks
is -12.80 which is statistically significant with the p-value less than 0.0001.
The difference between the means of Cooper's and sharp-shinned hawks is 8.22
which is also statistically significant with the p-value < 0.0001. The
difference of means between red-tailed and sharp-shinned hawks is 21.02 with the
p-value < 0.0001. Hence, we reject the null and accept the alternative. Finally,
we conclude that the variance between the three groups is not the same.

## Exercise 5.42

Do Exercise 5.42 as stated. Also do a Box-Cox analysis to see what response
transformation it would recommend. Choose a response transformation and do a
one-way ANOVA on the transformed response (Carat) vs. color. Analyze the
residuals and report all pairwise comparisons.

```{r}
data("Diamonds2")

Diam.summ = Diamonds2 %>%
    group_by (Color) %>%
    summarize (mean.Carat = mean (Carat), sd.Carat = sd (Carat))

Diam.summ$log.mean = log10 (Diam.summ$mean.Carat)
Diam.summ$log.sd = log10 (Diam.summ$sd.Carat)

Diam.summ

diamond_lm = lm(Diam.summ$log.sd ~ Diam.summ$log.mean)

ggplot() +
    geom_point(aes(x = Diam.summ$log.mean, y = Diam.summ$log.sd),
               color="tomato") +
    geom_line(aes(x = Diam.summ$log.mean,
                  y = predict(diamond_lm, list(Diam.summ$log.sd))),
              color="blue") +
    ggtitle("log(s) vs log(ave)") +
    theme(plot.title = element_text(hjust = 0.5)) +
    xlab("log(ave)") +
    ylab("log(s)")
```

\begin{itemize}
    \item[(a)]
        The points seem to suggest a \(\log x\) function. However, it is
        possible to eyeball a line.
    \item[(b)]
        We can eyeball the slope. It is in the range 1.4 - 1.5. We can say that
        it is approximately 1.45. After making a model and estimating the slope,
        we got that the slope is approximately 1.4008 \(\approx\) 1.4 which is
        not too far from our initial observation.
    \item[(c)]
        Since the slope is approximately 1.4, we get \(1 - \text{slope} = 1 -
        1.4 = -0.4\). Since the value is \(-0.4\), the reciprocal transformation
        of the form \(\frac{1}{\sqrt{\text{response}}}\) is suggested.
\end{itemize}

We will now proceed by performing the Box-Cox analysis to see what response
transformation it would recommend. We will then choose a response transformation
and do a one-way ANOVA on the transformed response (Carat) vs. color. Finally,
we will analyze the residuals and report all pairwise comparisons.

```{r}
carat_lm = lm(Carat ~ Color, Diamonds2)

# Residual analysis
par(mfrow = c(1,3))
plot(carat_lm, which = 1:3)

boxcox(carat_lm)
```

Box-Cox plot has the form of a flipped parabola \((f(x) = -x^2)\). The
\(\lambda\) (lambda) value is approximately 0 and is between -0.2 and 0.15 with
95% confidence. These observations suggest the non-normality of errors in the
linear model. Therefore, it is reasonable to perform the log transformation of
the response variable (Carat). This would help us normalize the errors as well
as address the non-linearity of the distribution.

It is important to note that the Residuals vs Fitted plot does not look good
(red line does not exactly follow the dotted line). Additionally, Normal Q-Q
also has some problems toward the tail of the plot.

```{r fig.height=3.5, fig.width=5}

# Perform the square root transform
lr = lm(log10(Carat) ~ Color, Diamonds2)

# Residual analysis
plot(lr, which = 1:3)

# Residual analysis
par(mfrow = c(1,3))
plot(lr, which = 1:3)
par(mfrow = c(1,1))

# ANOVA
s <- summary(emmeans(lr, pairwise ~ Color, adjust = "none"), infer = c(T, T))
s
```

After performing the log transformation, we have already gotten better with all
plots. Residuals vs Fitted is better as the red line follows the black dotted
line. Normal Q-Q plot has also improved and the normality assumption for ANOVA
is clearly met. The Scale-Location plot shows that the residuals are spread
equally along the ranges of predictors and that the variance is nearly constant.
Furthermore, the square root of Standardized Residuals show the decreasing
trend.

Our null hypothesis is that the differences of means across the groups are zero
and the alternative hypothesis is that at least one of differences of means is
different from 0. The $contrasts table shows the following results:

```{r}
s$contrast
```

Only two of the differences between means yields statistically significant
results and these are differences D - G (with -0.15529) and E - G (0.16528)
where p-value < 0.0001 in both cases. Hence, we reject the null and accept the
alternative hypothesis suggesting that means across the groups are different.