---
title: Homework \textnumero 1
author: David Oniani
date: \today
output: pdf_document
---

<!-- Do Exercises 5.14, 5.16, 5.18, 5.20, and 5.38. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise 5.14

\begin{itemize}
    \item[(a)] ANOVA is a natural generalization of the two-sample t test and
        hence, is suitable for comparing groups (their means). Therefore, this
        is not a reason not to use ANOVA.
    \item[(b)] Car age can be considered a quantitative variable and hence, it
        is not a reason not to use ANOVA. However, if we consider car age to be
        categorical, then using something along the lines of Logistic Regression
        would be better (but even then, it would not hurt trying ANOVA first).
        But yes, it can be a valid reason not to use ANOVA if we know for sure
        that car age is a categorical variable.
    \item[(c)] There is no equal sample size assumption when using ANOVA.
        However, equal sample size would be better as it would result in a
        well-behaved F-score. In conclusion, this is not a valid reason for not
        using ANOVA.
    \item[(d)] Since we took a random sample of 200 people, we can generalize.
        However, it is true that we might have gotten unlucky with these 200
        people and having a bigger sample would be more helpful. But, as already
        mentioned, randomization allows for generalization.
\end{itemize}

## Exercise 5.16

\begin{itemize}
    \item[(a)] Explanatory - diet (salmon, chicken, or beef). Response - average
        amount of time each dog sleeps per 24 hours for the next week.
    \item[(b)] This is a randomized experiment. The reason is that experimenter
        randomly assigned diets to 45 Border Collies and thus, has interfered
        with a way data is collected (in addition, randomized). This is
        different from an observational study where in lieu of random assignment
        or interference in data collection, experimenters merely observe the
        results of behaviors/events/etc.
    \item[(c)] If we assume that 45 Border Collies IS the population, then we
        have just taken 100\% sample from the population. The rest of the
        assumptions for ANOVA are met (including random sampling).
\end{itemize}

## Exercise 5.18

\begin{itemize}
    \item[(a)] Experimental units are 45 Border Collies.
    \item[(b)] Treatments are 3 types of diets (salmon, chicken, and beef).
    \item[(c)] The experiment would be balanced if each type of diet (3 in
        total) would be assigned to the same number of Border Collies.
\end{itemize}

## Exercise 5.20

\begin{itemize}
    \item Diets - 2 degrees of freedom (because there are 3 diets in total and
        as soon as we know any 2, the third one is not free to vary).
    \item Residual - 42 degrees of freedom (because the residual degrees of
        freedom is n - p where n is the sample size and p is the number of
        predictors - we have 45 - 3 = 42).
    \item Total - 44 (since Diets + Residual is 2 + 42 = 44).
\end{itemize}

## Exercise 5.38

```{r}
library (Stat2Data)
library (emmeans)

data ("Meniscus")
head (Meniscus)

# Boxplots
boxplot (Stiffness ~ Method, data=Meniscus)
boxplot (Stiffness ~ Method, data=Meniscus)

# ANOVA
men1 = lm (Stiffness ~ as.factor (Method), data=Meniscus)
summary (men1)
anova (men1)
summary (emmeans (men1, pairwise ~ Method, adjust="none"), infer=c(T,T))

# Residuals vs Fitted and Normal QQ
plot(men1, which=1)
plot(men1, which=2)
```

\begin{itemize}
    \item[(a)] \(H_0 : \mu_1 = \mu_2 = \mu_3\) and \(H_A :\) at least one
        \(\mu_i\) is different (where \(i \in \{1, 2, 3\}\)).
    \item[(b)] Notice that the methods are independent from each other and thus,
        the independence condition is met. The Residuals vs Fitted plot shows
        that the equality of variance condition is met (the red line
        approximately follows the dotted line) The QQ plot shows that the
        condition of normality is also met (dots approximately follow the line).
        Therefore, conditions for ANOVA are met for this data.
    \item[(c)] Notice that F value is 4.98. Hence, the average variance between
        groups is approximately 5 times larger than the average variance within
        groups. Now, given that the p-value is approximately 0.022 smaller than
        \(\alpha\) = 0.5 cutoff, we have enough evidence to reject the null
        hypothesis and accept the alternative which states that mean values of
        stiffness are different, and varies depending on the type of meniscus
        repair.
\end{itemize}