---
title: "Math 328 Chapter 7 HW"
author: "David Oniani"
date: "March 23, 2021"
output: word_document
---

<!-- Do Exercises 7.14, 7.16, 7.34, and 7.38, using R Markdown. -->

## Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(Stat2Data)
library(dplyr)
library (tidyr)
library(emmeans)
library(ggplot2)

# I like the minimal theme
theme_set(theme_minimal())

# Disable warnings (they clutter the document)
options(warn = -1)
```

## Exercise 7.14

It is clear that MSAB < MSB < MSA (A has 10s squared, B has 5s squared, and AB
has 4s squared) and each of the has 1 degree of freedom. Hence, MSAB < MSB < MSA
and we now need to find where MSE fits. SSE here equals to sum of square
residuals over the degrees of freedom which is 60 / 4 = 15. Now, since MSAB = 8
* 4^2 = 128, we have that MSE < MSAB. Finally, we have: MSE < MSAB < MSB < MSA.

## Exercise 7.16

It is clear that MSAB < MSA < MSB (B has 3s squared, A has 2s squared, and AB
has 1s squared) and each of the has 1 degree of freedom. Hence, MSAB < MSA < MSB
and we now need to find where MSE fits. MSE here equals to sum of square
residuals over the degrees of freedom which is 60 / 4 = 15. Now, since MSAB = 8
* 1^2 = 8 and MSA = 8 * 2^2 = 32, we have that MSAB < MSE < MSA. Finally, we
have: MSAB < MSE < MSA < MSB.

## Exercise 7.34

```{r}

# Dr. Phil's suggestion:
#     "For 7.34(c), I suggest plotting the data. Fitting a model using lm and
#     examining the parameter estimates could also be informative."

# Load the data
data("Swahili")

# (a)
modela = aov(Attitude.Score ~ factor(Province) * factor(Sex), data = Swahili)
summary(modela)

# (b)
par(mfrow = c(1 : 2))
plot(modela, which = c(1 : 2))

# (c)
modelc = lm(Attitude.Score ~ factor(School) * factor(Province), data = Swahili)
plot(modelc, which = c(1 : 2))
summary(modelc)
```

(a) Factors Province and Sex and both significant with the p-value being less
    than 2e-16. This means that attitudes toward Swahili vary significantly
    based on Province and Sex. The interaction between Province and Sex is also
    significant with the p-value of approximately 1.66e-13. This means that
    attitudes toward Swahili vary based on the interaction/relationship between
    Province and Sex (e.g., certain provinces have more people of a specific
    Sex). In terms of explaining the main effects, they do not really matter
    since we have an interaction. We need to first deal with the interaction,
    but the book does not suggest doing anything.

(b) The normality condition seems to be met. There are some points at the tail
    of the plot that deviate from the dotted line, but the Normal QQ does look
    normal overall. It seems like the variation is not constant. Ideally, the
    plot should show a random scattering of points above and below the reference
    line at a horizontal 0. This is not the case in Residuals vs Fitted plot
    where points are stacked across vertical lines. Hence, we conclude that the
    normality condition is met, while equal variance condition is not met.

(c) By just looking at Residuals vs Fitted plot, we can see that the equal
    variance condition is not met. Therefore, applying a two-way ANOVA is not
    appropriate in the first place. It is not a complete factorial design since
    equal sample size from each school is not enough. For the study to be a
    balanced complete factorial design, equal sample sizes must be taken for
    each of the possible factor combinations.

## Exercise 7.38

```{r}
# Dr. Phil's Comment:
#     " For 7.38, use the Oral exam score as the response variable
#       (not Written or Combine)."

# Load the data
data(Ricci)

# (a)
lra = lm(Oral ~ Position, data = Ricci)
sa = summary(emmeans(lra, pairwise ~ Position), infer = c(T, T))
sa$contrasts

# (b)
par(mfrow = c(1, 1))
with(Ricci, interaction.plot(Position, Race, Oral))

# (c)
lrc = lm(Oral ~ factor(Position) * factor(Race), data = Ricci)
par(mfrow = c(1, 3))
plot(lrc, which = c(1 : 3))
summary(aov(Oral ~ factor(Position) * factor(Race), data = Ricci))
```

(a) The difference between the means of Captain and Lieutenant is 6.02 with the
    p-value of approximately 0.012. Hence, the difference is not significant.

(b) Analyzing the interaction plot, the more nonparallel the lines are, the
    greater the strength of the interaction. In our case, there seems to be some
    interaction between Position and Race as the lines are not parallel. If we
    extend these lines in both sides (left and right), every pair of lines will
    cross each other. Hence, there could be a potential interaction between
    Position and Race variables.

(c) By just looking Residuals vs Fitted, we can conclude that the equal variance
    condition is not met. The red line has a noticeable skew in the left tail
    and deviates from the dotted line. The normality condition also does not
    seem to be met since the left part of the Normal QQ seems to show a
    significant deviation from the dotted line. The Scale-Location also seems to
    show a decreasing trend. Hence, we conclude that fitting a two-way ANOVA
    model is not appropriate (it might be appropriate after a response
    transformation however, but the book does not ask for this).

(d) We concluded that the two-way ANOVA model is not appropriate, but we will
    still comment on the results. Position and Race are both significant with
    p-values of approximately 0.0071 and 0.0001 respectively. Interaction
    between Position and Race, however, is not significant with the p-value of
    approximately 0.5095.