---
title: "Math 328 Chapter 8 HW"
author: "David Oniani"
date: "March 29, 2021"
output: word_document
---

<!-- Do Exercises 7.1, 7.2, 8.6, using R Markdown. -->

## Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(emmeans)
library(multcomp)
library(pwr)
```

## Exercise 7.1

```{r}
# k = g = 6
# f = sqrt(zeta/g*n) = sqrt(4*n/g*n) = sqrt(4/g) = sqrt(4/6) = sqrt(2/3)
# sig.level = 0.05
# power = 0.7
res1 <- pwr.anova.test(k = 6, f = sqrt(2/3), sig.level = 0.05, power = 0.7)
res1$n
```

Since we got that n = 3.646913, we should round it up (as the sample size cannot
be a floating point number) and we get n = 4. Hence, the answer is that the
smallest sample size is 4.

## Exercise 7.2

```{r}
# k = g = 3
# f = sqrt(((32/3 - 10)^2 + 2 * (32/3 - 11)^2) / 12) = sqrt(2/3 / 12) = sqrt(1/18)
# sig.level = 0.05
# power = 0.9
res2 <- pwr.anova.test(k = 3, f = sqrt(1/18), sig.level = 0.05, power = 0.9)
res2$n
```

Since we got that n = 76.93, we should round it up (as the sample size cannot be
a floating point number) and we get n = 77. Hence, the answer is that the sample
size is 77.

## Exercise 8.6

```{r}
# Load the data
load("oehlert.rdata")

# Get the right dataset
data <- pr08.6

# Make height, fert, and interval variables factors
data[, "height"]   <- factor(data[, "height"],   labels = c("1", "3", "6"))
data[, "fert"]     <- factor(data[, "fert"],     labels = c("0", "8", "16", "32"))
data[, "interval"] <- factor(data[, "interval"], labels = c("1", "3", "6", "9"))

# Report the structure
str(data)

# Fit the initial model
fit1 <- aov(cwt ~ .^2, data)

# Residual analysis
par(mfrow = c(1, 2))
plot(fit1)
par(mfrow = c(1, 1))

# Interaction plots
emmip(fit1, fert ~ interval)
emmip(fit1, height ~ interval)
emmip(fit1, height ~ fert)
```

The Residuals vs Fitted plot shows a constant variance. However, the red line
has some problems toward the right tail - it shifts down and does not follow the
black dotted line. That being said, overall, the Residual vs Fitted plot looks
good and the constant variance assumption does not seem to violated.

The Normal Q-Q plot shows that all, except for a few points in both tails,
follow the dotted line and thus, the normality assumption is not violated. That
being said, since at left tail, there are some number of points not aligning
across the dotted line, a response transformation could potentially help.

Scale-Location plot does not show a decreasing trend and shows that the variance
is constant.

Residuals vs Factor Levels does not show any problems either.

In terms of interactions plots, all three interaction plots show some degree of
interaction between the variables. The least degree of interaction seems to be
between variables height and fert. However, further analysis will show the
relationship between the variables in more detail.

Given our analysis, let us now perform a Box-Cox analysis in order to find an
appropriate power transformation for the response variable.

```{r}
# Box-Cox analysis for the power transformation
MASS::boxcox(fit1, lambda = seq(0, 1, 0.2))
```

From the plot, we can see that the lambda value is approximately 0.5 meaning
that the response should be raised to 0.5 power and the model should then be
refit. This is a square root transformation of the response.

```{r}
# Refit the model, applying the right power transformation
fit2 <- aov(sqrt(cwt) ~ .^2, data)

# Residual analysis
par(mfrow = c(1, 2))
plot(fit2)
par(mfrow = c(1, 1))
```

Even after applying the transformation, the Residuals vs Fitted plot looks
a bit better and the downward trend at the right tail is not as significant.

The Normal Q-Q plot looks a bit better and the normality assumption is
satisfied.

Scale-Location plot has a small improvement and still shows constant variance.

Residuals vs Factor Levels plot still looks good.

Even though we have performed a response transformation, it did not improve our
model significantly as the model itself was fairly good from the very get-go.

Let us see the summary and if any, report significant interactions.

```{r}
# Report the summary
summary(fit2)

# Plot ONLY the significant interaction effects
emmip(fit2, height ~ interval)
emmip(fit2, fert ~ interval)
```

It seems like variable fert is significant with the p-value of 3.51e-11.

Variable interval is also significant with the p-value of 5.86e-13.

Two interactions: height:interval and fert:interval are significant with the
p-values of 0.043 and 0.040 respectively.

The plots of the significant interactions are also shown.

```{r}
cld(emmeans(fit2, ~ height | interval), letters=LETTERS)
cld(emmeans(fit2, ~ fert   | interval), letters=LETTERS)

emmip(fit2, ~ height:interval)
emmip(fit2, ~ fert:interval)
```

Above find the appropriate pairwise comparisons for the significant effects.

Let us now analyze emmeans with height and interval interaction.

In the first interval, means are approximately equal to each other.

In the third interval, height = 3 and height = 6 have the highest means that are
also approximately equal to each other. height = 1 has the mean of 10.46, which
is noticeably smaller than 11.17 or 11.20.

In the sixth interval, height = 1 (13.31) and height = 6 (13.12) have higher
mean values than height = 3 (12.29).

In the ninth interval, height = 3 has the highest mean value of 14.20. Means at
height = 1 and height = 6 and close and equal to 13.74 and 13.59 respectively.

Let us now analyze emmeans with fert and interval interaction.

Interestingly, in all intervals, we see clearly that the higher fert values have
higher corresponding emmean values. Also, the bigger the interval, the bigger
the average response (emmean). The plots also suggests the same.