---
title: "Chapter 18-19 Homework"
author: "David Oniani"
date: "May 1, 2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# For testing, put the Oehlert.Rdata file in the folder shown by: getwd()
# For knitting, put a copy of Oehlert.Rdata in the same folder as this R Markdown file 
load ("oehlert.rdata")
library (tidyr)
library (ggplot2)
library (rsm)
```

## Problem 18.6

Silicon wafers for integrated circuits are grown in a device called a susceptor,
and a response of interest is the thickness of the silicon. Eight factors, each
at two levels, were believed to contribute: rotation method (A), wafer code (B),
deposition temperature (C), deposition time (D), arsenic flow rate (E), HCl etch
temperature (F), HCl flow rate (G), and nozzle position (H). A $2^{8-4}$ design
was run with generators I = ABCD = BCEF = ACEG = BCEH.

### Main Effect plots

```{r fig.height=5, fig.width=7}
str (pr18.6)
ggplot(pivot_longer (pr18.6, cols = 1:8, names_to = "Factor", values_to = "Level"), 
       aes(x=Level, y=thickness)) + geom_point() +
  stat_summary (fun=mean, geom="line", aes(group=Factor)) +
  facet_wrap(~Factor, scales = 'free_x')
```

What do you notice in these plots?

The plot shows the main effects for each of the eight factors. Bigger slopes
correspond to bigger main effects. Based on the plot, it appears that factors B
and E have the smallest main effects (i.e., lines are approximately parallel to
the x-axis [i.e., line is flat]). Factors A (negative direction) and C (negative
direction) seem to have main effects bigger than factors B and E as the lines
are less parallel to the x-axis than for factors B and E (considering absolute
values/magnitudes of the effects as the direction for some effects is positive
and for some effects, it is negative). Factors F, G, and H come next with the
lines that are clearly not parallel to the x-axis. Finally, factor D has the
biggest slope (i.e., take the absolute value of the slope) and has the largest
main effect. That being said, the direction of this main effect is negative. As
for the largest positive main effect, it seems to be factor H. Therefore, we
have the following tentative main effects ordering (based on absolute
values/magnitudes of the effects): E, B, C, A, G, F, H, D.

### Fit a model with all main effects and 2-factor interactions:

```{r}
fit18.6 = lm (thickness ~ (A+B+C+D+E+F+G+H)^2, data=pr18.6)
summary (fit18.6)

# See if H and F are aliased with the C, D, E, and F interactions.
alias_check_h = lm(H ~ B * C * E, data=pr18.6)
summary(alias_check_h)

alias_check_f = lm(F ~ B * C * E, data=pr18.6)
summary(alias_check_f)
```

Note that the H main effect is not estimable. Also note that none of the
interaction effects involving H are estimable.

Use the defining contrast, BCEH = BCEF, and defining contrast algebra to show
that the main effect for H is confounded (aliased) with the main effect for F.

Given BCEH = BCEF, let us multiply both sides by BCE. We get, BCEBCEH = BCEBCEF.
Applying the commutative property, we get BBCCEEH = BBCCEEF. Using the fact that
the same letters cancel each other, we get H = F and we conclude that the main
effect for H is confounded (aliased) with the main effect for F.

Alternatively, we could do this without using defining contrast algebras. We can
take a look at summaries for the models H ~ B * C * E and F ~ B * C * E. In both
cases, only one interaction B:C:E is significant with the Estimate of 1 and a
very significant p-value of less than 2e-16. In both cases, we also get the
R-squared value of 1. Therefore, we can conclude that the main effect for H is
confounded (aliased) with the main effect for F.

### Second model

Remove H and refit. Include the A:B:E interaction, which is estimable.

```{r}
fit18.6b = lm (thickness ~ (A+B+C+D+E+F+G)^2 + A:B:E, data=pr18.6)
summary (fit18.6b)
```

Make a normal Q-Q plot of the effects.

```{r fig.height=3.5, fig.width=4}
effs18.6b = fit18.6b$effects [2:fit18.6$rank]
qqnorm (effs18.6b)
qqline (effs18.6b)
abline (h=0.5, lty=2)
effs18.6b [abs (effs18.6b) > 0.5]
```

Which effects are significant?

There is only one effect that is significant. It is the effect D and its value
is 1.6125.

### What effects are confounded with factor D?

Use defining contrast algebra for each of these relations to determine the
effects (main or interaction effects) that are confounded with the main effect
of D (hint - multiply both sides by ABC in each expression):

* ABCD = BCEF
* ABCD = ACEG
* ABCD = BCEH

Given ABCD = BCEF, let us multiply both sides by ABC. After regrouping, we get
AABBCCD = ABBCCEF which gives us D = AEF. Thus, we got that the three-way
interaction AEF is confounded with the main effect of D.

Given ABCD = ACEG, let us multiply both sides by ABC. After regrouping, we get
AABBCCD = AABCCEG which gives us D = BEG. Thus, we got that the three-way
interaction BEG is confounded with the main effect of D.

Given ABCD = BCEH, let us multiply both sides by ABC. After regrouping, we get
AABBCCD = ABBCCEH which gives us D = AEH. Thus, we got that the three-way
interaction AEH is confounded with the main effect of D.

## Problem 19.5

Curing time and temperature affect the shear strength of an adhesive that bonds
galvanized steel bars. The following experiment was repeated on 2 separate days.
Twenty-four pieces of steel are obtained by random sampling from warehouse
stock. These are grouped into twelve pairs; the twelve pairs are glued and then
cured with one of nine curing treatments assigned at random. The treatments are
the three by three factorial combinations of temperature (375, 400, and 450
degrees F, coded -1, 0, 2) and time (30, 35, or 40 seconds, coded -1, 0, 1).
Four pairs were assigned to the center point, and one pair to all other
conditions. The response is shear strength (in psi, data from Khuri 1992):

| Temp. | Time | Day 1 | Day 2 |
|-------|------|-------|-------|
| -1    | -1   | 1226  | 1213  |
| 0     | -1   | 1898  | 1961  |
| 2     | -1   | 2142  | 2184  |
| -1    | 0    | 1472  | 1606  |
| 0     | 0    | 2010  | 2450  |
| 0     | 0    | 1882  | 2355  |
| 0     | 0    | 1915  | 2420  |
| 0     | 0    | 2106  | 2240  |
| 2     | 0    | 2352  | 2298  |
| -1    | 1    | 1491  | 2298  |
| 0     | 1    | 2078  | 2531  |
| 2     | 1    | 2531  | 2609  |
|       |      |       |       |

```{r}
str (pr19.5)
tmp_time = pr19.5$time
tmp_temp = pr19.5$temp
pr19.5$temp = tmp_time
pr19.5$time = tmp_temp
str(pr19.5)
plot (pr19.5, col=pr19.5$day)
```

Plot the data:

```{r fig.height=3.5, fig.width=6}
ggplot (pr19.5, aes (x=time, y=strength, color=factor(temp))) + geom_point() +
  facet_wrap (vars(day), labeller="label_both") +
  stat_summary (fun=mean, geom="line", aes(group=temp))
```

(Note: No interpretation needed for the plot above.)

### Response surface model:

Fit a second-order response surface model and include day as a block effect.

```{r}
fit19.5 = rsm (strength ~ day + FO(time, temp) + SO(time, temp), data=pr19.5)
summary (fit19.5)
```

Which effects are significant?

The main effects day, time, and temp are significant with the p-values of
approximately 0.001, 6.535e-05, and 2.514e-07 respectively. The intercept is
significant as well, with the p-value of approximately 1.409e-11. Finally,
temp^2 is also significant with the p-value of approximately 0.0003.

### Test for lack of fit

Based on the output above, is there significant lack of fit?  Include the
p-value for the lack of fit test.

There is not a significant lack of fit since the p-value is approximately 0.730,
which is way above the 0.05 cutoff.

### Check the residuals:

```{r fig.height=3.4, fig.width=7}
par (mfrow=c(1,2))
plot (fit19.5)
```

Interpret the residual plots:

Residuals vs Fitted plot shows that the variance is equal since the points are
scattered randomly above and below the reference line at 0. That being said, the
red line does not follow the dotted line. However, this does not change the fact
that we have equal variance.

Normal Q-Q plot shows that the distribution is approximately normal since most
of the points follow the dotted line. There is an evidence of some non-normality
at both tails of the Normal Q-Q (slightly heavier right tail), but, overall, the
plot does not show non-normal patterns.

Scale-Location plot shows equal variance and, to some degree, further
corroborates the hypothesis from Residuals vs Fitted plot.

Residuals vs Leverage does not show any noticeable outliers. While we do see the
Cook's contours, none of the points are beyond them.

```{r fig.height=3.5, fig.width=4}
plot (strength ~ fit19.5$fitted.values, data=pr19.5)
abline (0, 1)
```

### Analysis conclusion

```{r fig.height=3.5, fig.width=5}
ggplot (pr19.5, aes (x=time, y=strength, color=factor(temp), shape=factor(day))) + 
  geom_point() +
  stat_summary (fun=mean, geom="line", aes(group=temp))
```

Given these modeling results, and the data plot just above, what values of time
and temperature would you choose to maximize strength. Stay within the range of
values tested for those factors.  You may state a specific value for time and
for temperature or a range of values.  Use the original scales for time and
temperature, as stated at the beginning of the problem.

The highest value for strength is approximately 2550. This value is obtained
when time is 1 (coded) and temperature is 2 (coded). Recall, that time time was
coded -1, 0, 1 for 30, 35, and 40 seconds respectively and the temperature
was coded -1, 0, and 2 for 375, 400, and 450 degrees F. Hence, in order to
maximize the strength, we would choose 40 seconds and 450 degrees F.
